### 2020-01-02 docs/thesis-project/article.tex
Update article.tex

\section{Data Redundancy}\label{sec:dataredundancy}
In DFS, not losing data is of the utmost importance. Particularly, peer availability in P2P networks is ever-changing and not guaranteed, and thus, availability, and even durability of files are at risk. A \textbf{\textit{durable file}} is one that, once put into the system, is not lost due to failures, whereas availability means that a user can access it promptly. Durability is accomplished by employing file or block-level \textbf{\textit{replication}} or alternatively, using \textbf{\textit{erasure coding}} techniques (\textit{coding} for short). Hybrid approaches are also possible. Replication has the advantage of having a straightforward and less resource-intensive recovery model, on the other hand, coding has a better \textit{expansion factor}, i.e., can provide the same or even increased durability at a lower storage overhead. Because our proposal focuses on the survivability of files in P2P networks built on top of personal computers, using swarm guidance, where resources may be limited, we focus on surveying coding, mentioning raised concerns and inherent disadvantages of this technique.

Two parameters specify some of the most widely used coding algorithms, the number of data symbols \textit{k} to be encoded, and the number of coded symbols \textit{n} to be produced, both assumed to be in a finite field $GF(2^w)$ and these are referred as \textit{(n, k) erasure-codes}. The fundamental idea, is that a file of size $S$ is divided into $k$ equally sized fragments and encode them into $n$ encoded fragments, allowing the original file to recovered from any set of encoded-fragment with count $k$. Systems that use these and other more sophisticated coding are evaluated under some of the following metrics, the \textbf{\textit{repair-bandwidth}}, i.e., the number of bits communicated in the network during normal and repair operations, the \textbf{\textit{disk I/O}} which is the number of bits read from disk during each repair, the \textbf{\textit{repair locality}} which is the number of peers that would be involved in the repair process; Since coding algorithms are slow processes CPU cycles, XOR operation counts and cache misses are metrics often researched as well \cite{fast_coding}, when the main interest is tied with load-balancing and cost savings. We take particular interest in the first metric because, in general, coding may lead to unreasonable bursts in bandwidth consumption when availability requirements, in very dynamic systems, are high \cite{coding-problems}, even for today's standards. Whenever a peer fails, all files he held need to be quickly recovered by some peer who needs to gather enough fragments from possibly many different peers. Such burst in consumption may lead to delays or even failure of the repair process due to physical link capacity between peers, who are involved in the repair process, or even throughput constraints enforced by each peer. When it comes to redundancy in a distributed storage systems, one fundamental question is deciding when to replicate or recover data; this is often called the replica-control problem.

There are two main approaches, reactive and proactive. Reactive approaches are the least complex, and consist of recovering data whenever a failure is detected; they suffer the most from bandwidth bursts, and mitigations to this problem include use of predictive models and thresholds to avoid unnecessary recoveries \cite{lifetime-reactive, efficient-replica-mng-reactive}. Proactive approaches seek to smooth bandwidth consumption by injecting new redundancy data into the network overtime at a fixed-rate \cite{proactive-rep, reliability-without-availability}.

The most widely known coding algorithms belong to the \textit{Maximum Distance Separable} (MDS) class, this class is likely to offer the best reliability-redundancy trade-off. Regardless of the chosen approach, research \cite{network-coding-for-dss} suggests that for coding to be competitive in distributed storage systems, one should seek to minimize these costs, while maximizing redundancy to only the amount necessary to ensure a specific service guarantee. They identify \textit{Minimum Bandwidth Regenerating} (MBS), and all codes in between these two ends of the spectrum as \textit{regenerating codes}, the differences between codes on the spectrum depend on the values such has \textit{n}, \textit{k} and on the implementation of the algorithms themselves. Shokrollahi \textit{et al.} introduces raptor codes \cite{raptor-codes}, which are a linear-time coding and decoding extension of LT codes. LT codes belong to the class of rateless codes, i.e., a potentially infinite sequence of encoded fragments can be generated from a given data source. Furthermore, the original data is recoverable from any subset of the encoded fragments of size equal to or slightly larger than original data size; These rateless code implementations are of particular importance because they are scalable with regards to the machine and network resources,  and fault-tolerant concerning dynamic and heterogeneous network environments. Finally, Zhou \textit{et al.} \cite{fast_coding} perform a study on state of the art techniques that improve coding efficiency through bitmatrix optimization, vectorization, and scheduling and prove that when used in conjunction much better levels of performance can be delivered, e.g., 552.27\% when compared to simple MDS implementations, in particular, the Reed-Solomon algorithm.

>>>>

\section{Data Redundancy}\label{sec:dataredundancy}
In DFS, not losing data is of the utmost importance. Particularly, peer availability in P2P networks is ever-changing and not guaranteed, and thus, availability, and even durability of files are at risk. A \textbf{\textit{durable file}} is one that, once put into the system, is not lost due to failures, whereas availability means that a user can access it promptly. Durability is accomplished by employing file or block-level \textbf{\textit{replication}} or alternatively, using \textbf{\textit{erasure coding}} techniques (\textit{coding} for short). Hybrid approaches are also possible. Replication has the advantage of having a straightforward and less resource-intensive recovery model, on the other hand, coding has a better \textit{expansion factor}, i.e., can provide the same or even increased durability at a lower storage overhead. Because our proposal focuses on durability of files in P2P networks built on top of personal computers, where resources may be limited, we survey only coding, mentioning raised concerns and inherent disadvantages of this technique.

Commonly coding algorithms receive two parameters, the number of data symbols \textit{k} to be encoded, and the number of coded symbols \textit{n} to be produced; these are referred to as \textit{(n, k) erasure-codes}. The fundamental idea, is that a file of size $S$ is divided into $k$ equally sized fragments then turned into $n$ encoded fragments, allowing the original file to recovered from any set of encoded-fragment with count $k$. Systems that use (n, k) or more sophisticated codes are evaluated under some of the following metrics: the \textbf{\textit{repair-bandwidth}}, i.e., the number of bits communicated in the network during normal and repair operations, the \textbf{\textit{disk I/O}} which is the number of bits read from disk during each repair, the \textbf{\textit{repair locality}} which is the number of peers that would be involved in the repair process; Since coding is a slow process CPU cycles, XOR counts and cache misses are often evaluated as well\cite{fast_coding}. We take particular interest in the first metric because, in general, coding may lead to unreasonable bursts in bandwidth consumption when availability requirements, in very dynamic systems, are high\cite{coding-problems}, even for today's standards. Whenever a peer fails, all files he held need to be promptly recovered by some peer who needs to gather enough fragments from possibly many different peers. Such burst in consumption may lead to delays or even failure of the repair process due to physical link capacity between peers, who are involved in the repair process, or even throughput constraints enforced by each peer; this leads us to the second key question, which is: at what time should data be replicated or recovered?\footnote{Literature often refers to this question as the replica-control problem} Reactive approaches are the least complex and consist of recovering data whenever a failure is detected; they suffer the most from bandwidth bursts, and burst mitigation includes the use of predictive models and thresholds to avoid or delay recovery\cite{lifetime-reactive, efficient-replica-mng-reactive}. Proactive approaches seek to smooth bandwidth consumption by injecting new redundancy data into the network over time at a fixed or variable rate \cite{proactive-rep, reliability-without-availability}. Concerning algorithm classification, the most widely known belong to the \textit{Maximum Distance Separable} (MDS) class, which likely offers the best reliability-redundancy trade-off. However, research \cite{network-coding-for-dss} suggests that for coding to be competitive in DFS, we need to minimize costs inherent to the MDS class, while keeping redundancy levels to only the amount necessary to ensure specific service guarantees. The same research identifies a \textit{Minimum Bandwidth Regenerating} (MBS) class and refers to codes in between these two as \textit{regenerating codes}. There is no standard for classification, and it often depends on the obtained trade-offs and thus depends on chosen $n, k$ values, possibly some extra parameters, and actual algorithmic implementation. Shokrollahi \textit{et al.} introduces raptor codes \cite{raptor-codes}, which are a linear-time coding and decoding extension of LT codes, belonging to the rateless code class. Rateless codes are characterized by the property that a potentially limitless sequence of encoded fragments can be generated from a given source, and the original data is recoverable from any subset of the encoded fragments of size equal to or slightly larger than original data size; Rateless codes differ from MDS codes because they are scalable with regards to both machine and network resources, and fault-tolerant concerning dynamic and heterogeneous network environments. Finally, Zhou \textit{et al.} \cite{fast_coding} carry out a study on state of the art techniques that improve coding efficiency through bitmatrix optimization, vectorization, and scheduling, proving that when used in conjunction, fragment generation and data reconstruction can be up to 552.27\% faster.
